%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
  {} % Role
  {Stock Analysis Demo} % Title
  {} % Location
  {} % Date(s)
  {
    \begin{cvitems}
      \item {Built an A-share stock analysis demo with FastAPI, SQLAlchemy Async, and PgQueuer, making data ingestion, analysis, and task execution asynchronous as a basic backend pipeline for AI applications.}
      \item {Implemented a YAML-based rule engine and integrated CNInfo and Yahoo Finance data pipelines with retry, rate limiting, and caching mechanisms.}
      \item {Implemented an agent interaction workflow based on LangGraph + RAG + SSE, integrated tools through MCP, and added Redis, PostgreSQL, Docker/K8s, and observability with OTel/Prometheus/Grafana.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {} % Role
  {Valgrind Porting and Adaptation} % Title
  {} % Location
  {} % Date(s)
  {
    \begin{cvitems}
      \item {Added LoongArch64 support to Valgrind, including core component porting and translation of key instructions.}
      \item {Followed implementation paths from other architectures to incrementally adapt runtime and system-related modules, and built regression tests for validation.}
      \item {Diagnosed and fixed an immediate-value loading instruction issue under specific conditions by narrowing test cases and constructing minimal failing cases.}
      \item {Completed the initial build within one week and reached an initially usable state within one month, passing hundreds of regression tests.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {} % Role
  {OpenStack Porting and Deployment Adaptation} % Title
  {} % Location
  {} % Date(s)
  {
    \begin{cvitems}
      \item {Contributed to MIPS support for OpenStack Nova and adapted the DevStack deployment workflow for deployment and validation on Fedora MIPS.}
      \item {Started from existing x86 automated deployment scripts, decomposed the multi-component deployment process, and incrementally resolved key blocking points.}
      \item {Fixed and validated compatibility and deployment issues of core components, bringing up the core service workflow within one month.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {} % Role
  {System Software Adaptation and Tooling} % Title
  {} % Location
  {} % Date(s)
  {
    \begin{cvitems}
      \item {Contributed Linux kernel patches and adapted system components including klibc, Kcov, and RT-Thread on LoongArch.}
      \item {Participated in hardware-related integration work (e.g., LS2K0300), supporting software stack bring-up and debugging on target platforms.}
      \item {Developed a VSCode syntax highlighting extension for LoongArch assembly to improve development and debugging efficiency.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {} % Role
  {CI/CD Optimization for Documentation Collaboration} % Title
  {} % Location
  {} % Date(s)
  {
    \begin{cvitems}
      \item {Designed and implemented a CI/CD workflow to address low review efficiency and limited preview capability in external documentation collaboration.}
      \item {Enabled real-time PR previews and automatic contributor attribution, improving both community collaboration experience and internal review efficiency.}
      \item {Helped establish a unified documentation collaboration workflow that received positive feedback from the community and was later adopted by other teams.}
    \end{cvitems}
  }
%---------------------------------------------------------
\end{cventries}
